---
title: "STAT 433 HW 1"
output: html_document
---
```{r}
library(dplyr)
library(nycflights13)
library(ggplot2)
```


#1. How many flights have a missing dep_time? What other variables are missing? What might these rows represent?
```{r}
summary(flights)
```
##Accoring to the summary, there are 8255 flights missing "dep_time" which marked as NA in the database. "dep_delay", "arr_time", "arr_delay", and "air_time" have missing or NA data. For thoes missing variables, we speculate that 1: the flight may get canceled; 2: departured but back to the origin airport; 3: Fail to collect the data. 

#2. Currently dep_time and sched_dep_time are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.
```{r}
dep_min = (flights$dep_time%%100) + 60*(flights$dep_time%/%100)
shed_dep_min = (flights$sched_dep_time%%100) + 60*(flights$sched_dep_time%/%100)
```

#3. Look at the number of canceled flights per day. Is there a pattern? Is the proportion of canceled flights related to the average delay? Use multiple dyplr operations, all on one line, concluding with ggplot(aes(x= ,y=)) + geom_point()
```{r}
flights %>% 
  group_by(month,day) %>% 
  summarize(delay = mean(dep_delay, na.rm = T),
            cancelled = sum(is.na(dep_time)/n())) %>% 
  ggplot(mapping = aes(x = delay, y = cancelled)) + geom_point()
```
#According to the ggplot, there is no strong relationship between the proportion of canceled flights and average delays. 

